A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-10-18 manuscript/manuscript.tex
finished abstract

Mastering the ``arcana of neuroimaging analysis'', the obscure knowledge required to apply an
appropriate combination of software tools and parameters to analyse a given neuroimaging dataset,
is a time consuming process. Therefore, it is typically not feasible to invest the additional effort
required to implement analysis workflows in a form that generalises across the various acquisition
parameters, data storage conventions and computing environments in use at different research sites,
which limits the reusability of published workflows.

We present a novel software framework, \emph{Abstraction of Repository-Centric ANAlysis (Arcana)}, which enables
the development of complex, ``end-to-end'' workflows that are adaptable to new analyses and
portable to a wide range of computing infrastructures. Analysis templates for specific image types (e.g. MRI contrast)
are implemented as Python classes that specify potential derivatives and modular pipelines to derive them.
Arcana retrieves data from imaging repositories, which can be BIDS datasets, XNAT instances or plain directories, and
stores selected derivatives back into a repository with provenance data for reuse by subsequent analyses.
Pipelines are constructed using Nipype and can be processed on local or on high performance computing environments,
enabling a smooth transition from locally developed prototypes to large-scale deployment. we have created a framework that handles all the tedious aspects and allows researchers to focus on the analysis design
it is flexible to allow researchers to collaborate

>>>>

Mastering the ``arcana of neuroimaging analysis'', the obscure knowledge required to apply an
appropriate combination of software tools and parameters to analyse a given neuroimaging dataset,
is a time consuming process. Therefore, it is not typically feasible to invest the additional effort
required generalise workflow implementations to accommodate for the various acquisition parameters,
data storage conventions and computing environments in use at different research sites,
limiting the reusability of published workflows.

We present a novel software framework, \emph{Abstraction of Repository-Centric ANAlysis (Arcana)},
which enables the development of complex, ``end-to-end'' workflows that are adaptable to new analyses and
portable to a wide range of computing infrastructures. Analysis templates for specific image types (e.g. MRI contrast)
are implemented as Python classes, which specify a range of potential derivatives and analysis methods.
Arcana retrieves data from imaging repositories, which can be BIDS datasets, XNAT instances or plain directories, and
stores selected derivatives back into a repository with provenance data for reuse by subsequent analyses.
Workflows are constructed using Nipype and can be executed on local workstations or in high performance
computing environments without alteration. Generic analysis methods can be consolidated within a common
base classes to facilitate code-reuse and collaborative development, which can be specialised for study-specific
requirements via class inheritance. Therefore, Arcana provides a platform to develop unified neuroimaging
workflows that can be reused across many research sites and studies.
